The Evolution of Manufacturing Ecosystem in Cloud Manufacturing Architecture

### 2016-09-08 design.tex
modify the abstract

A single order consists of a set $\mathcal{T}_i = \left\{ t_{i1},t_{i2},\dots\right\}$ of tasks, the tasks are interrelated by kinds of constraints. First, precedence constraints force task $t_{ij}$ not to be started before all its immediate predecessors $\mathcal{P}_{ij}$. Second, performing the tasks requires resources with limited capacities. Third, resources cooperation requires all the task-parts in active status.
A single resource($mr_k$) belongs to only one type. While being processed, task $t_{ij}$ requires $q_{\alpha,ij}$ units capacity of the resources with each type $\alpha\in\mathcal{A}_{ij}$ during every period of its non-preemptable duration $p_{ij}$. Each resource $mr_k$ has a limited capacity $C_{k,\tau}$ and available capacity $A_{k,\tau}$ at any point in time $\tau$. This plan is much like the settings in RCPSP\cite{Kolisch1999} except that the task here need multiple types of resource simultaneously.

@@

The first thing of incubation is to publish a job named service-call, which is similar with task except for the capacity dominance feature , which means capacity of selected resource will not be returned back to after the performance of service-call. The process result of one service-call is manufacturing service, which is actually a set of resources that may come from selected providers in the system, it's possible for more than one resource with same type to make contribution to the formation of one service. No more cooperate and assembly procedure are part of pros of service and product quality will no more restricted to the worst quality of resources for the complementary effect, while the cons of service include that service can only perform specified task.
Now we can mark task and service-call as job, resource and service as machine.

@@

\subsection{Provider schedule the jobs in machine} % (fold)
\label{sub:schedule_the_jobs_in_machine}
In order to reduce the idle rate, provider will schedule the inactive jobs on their machines. Since the schedule in service is a single machine scheduling problem that not on  what we focus in this study, we only discuss the job scheduling in resource. Since the  resource capacity dominance feature of service-call, it's necessary to suspend service-call in inactive status until all the job before it in $\mathcal{L}_{k,\tau}$ are finished, at the meantime, all the job after service-call should be stay in inactive status until the service-call is finished, as shown in \autoref{fig:simplejoblist}, service-call likes partition plate in $\mathcal{L}_{k,\tau}$.  
\begin{figure}[htbp]
	\centering
	\resizebox{.7\textwidth}{!}{\input{figures/service-call}}
	\caption{Simple illustration for one $\mathcal{L}_{k,\tau}$}
	\label{fig:simplejoblist}
\end{figure}
Therefore, the we just need to schedule the tasks before the first service-call in $\mathcal{L}_{k,\tau}$ when one of the active job in $\mathcal{G}_{k,\tau}$ was finished at $\tau_0$, we denote the set of schedule task at this time as $\mathcal{L}^{(s)}_{k,\tau_0}$

Specifically, a simple instance with configuration \autoref{tab:simplejobconfiguration} and schedule chart \autoref{fig:scheduleChart} will elucidate the setting.
This instance makes some simplification in the subscript fields in order to emphasize the resource cooperation, all the job performance can only be started when all its parts are in semi-activate status, the shadow in the figure shows the waiting period between the status transition. Horizontal dotted line constrained the available capacity of the resource for the subsequent jobs. Each finish of service-call will make the horizontal dotted line lower and it will never get higher again unless the related service is repealed.

\begin{table}[htbp]
  \centering
  \scriptsize
  \caption{Simple job configuration}
    \begin{tabular}{cccccc}
    \toprule
    \multicolumn{1}{c}{\multirow{2}[0]{*}{ Job}} & \multicolumn{3}{c}{Need Resource Capacity} & \multicolumn{1}{c}{\multirow{2}[0]{*}{Release Time}} & \multicolumn{1}{c}{\multirow{2}[0]{*}{Process Duration}} \\
    \multicolumn{1}{c}{} & $Type_1$ & $Type_2$ & $Type_3$ & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} \\
    \midrule
    $t_1$ & 0     & 5     & 7     & 0     & 7 \\
    $t_2$ & 7     & 5     & 7     & 4     & 5 \\
    $t_3$ & 6     & 0     & 5     & 2     & 3 \\
    $t_4$ & 9	 & 4  & 6 & 1 &2 \\
    $t_5$ & 1 & 0 & 3 & 2 & 3\\
    $sc_1$ & 0     & 0     & 3    & 1     & 1 \\
    $sc_2$ & 2     & 7     & 6     & 3     & 1 \\
    \bottomrule
    \end{tabular}%
  \label{tab:simplejobconfiguration}%
\end{table}%
\begin{figure}[htbp]
	\centering
	\normalsize
	\resizebox{.8\textwidth}{!}{\input{figures/scheduleChart}}
	\caption{Simple instance schedule chart with 4 resources in 3 different types}
	\label{fig:scheduleChart}
\end{figure}

In every single resource, a schedule is given by a vector of ideal finish times $\bm{f}^{(s)} = \left[f_1^{(s)}, f_2^{(s)},\dots,f^{s}_n\right]$,$n=\abs{\mathcal{L}^{(s)}_{k,\tau_0}\cup\mathcal{H}^{(s)}_{k,\tau_0}}$. Since the task in $\mathcal{L}^{(s)}_{k,\tau_0},\mathcal{H}^{(s)}_{k,\tau_0}$ and $\mathcal{G}_{k,\tau_0}$ may come from different orders, we here use the single uniform subscript $j$ to distinguish these tasks and their related variables, we ignore the type subscript $\alpha$ because all the job assigned here are already type matched. The schedule model is:

@@

\subsection{Metabolism mode} % (fold)
\label{sub:metabolism mode}
Metabolism mode is one extension on the original mode for platform operator to control the number of individual in the system by both restrict the arrival and eliminate the current members. As shown in \autoref{fig:metabolismmode}, 
\begin{figure}[htbp]
    \centering
    \resizebox{0.85\textwidth}{!}{\input{figures/metabolism}}
    \caption{Metabolism mode}
    \label{fig:metabolismmode}
\end{figure}
machine scarcity is the control variable that can be defined as $\sum_jq_{\alpha,ij} - \sum_kC_{k,\tau}$ for resource in type $\alpha$ and the sum of task minus the sum of service in each type.

Platform restrict the arrival of new machine by block the registration, eliminate the current machine by their quality and owner's rank. Rank value is initialized to $0$ and will be changed by demander's review after the finish of task:
\begin{subnumcases}{}
rank := rank +
\frac{\left( p_{ij}\cdot q_{ij} \right) \left( \delta_{ij}-\gamma_{ij} \right)}{e^{\left(f_{ij} - p_{ij} -r_{ij}\right)}} & $k\in\bm{k}$\\
\delta_{ij} = \min_{k\in\bm{k}}\left\{ \delta_k \right\} & \\
\delta_k \sim \mathcal{N}\left(\mu_k,\sigma_k^2 \right) & $k\in\bm{k}$
\end{subnumcases} 
The change of rank value can be determined by:
\begin{equation}
	rank := rank + \frac{ \left(\sum_{q\in\bm{q}_l}p_{ij}\cdot q \right)\left( \Delta_l -\gamma_{ij}\right) }{ e^{\left( f_{ij} - p_{ji} -r_{ij} \right)} }
\end{equation}

>>>>

A single \textbf{order} consists of a set $\mathcal{T}_i = \left\{ t_{i1},t_{i2},\dots\right\}$ of tasks, the tasks are interrelated by kinds of constraints. First, precedence constraints force \textbf{task} $t_{ij}$ not to be started before all its immediate predecessors $\mathcal{P}_{ij}$. Second, performing the tasks requires resources with limited capacities. Third, resources cooperation requires all the task-parts in active status.
A single \textbf{resource}($mr_k$) belongs to only one type. While being processed, task $t_{ij}$ requires $q_{\alpha,ij}$ units capacity of the resources with each type $\alpha\in\mathcal{A}_{ij}$ during every period of its non-preemptable duration $p_{ij}$. Each resource $mr_k$ has a limited capacity $C_{k,\tau}$ and available capacity $A_{k,\tau}$ at any point in time $\tau$. This plan is much like the settings in RCPSP\cite{Kolisch1999} except that the task here need multiple types of resource simultaneously.

@@

The first thing of incubation is to publish a job named \textbf{service-call}, which is similar with task except for the capacity dominance feature , which means capacity of selected resource will not be returned back to after the performance of service-call. The process result of one service-call is manufacturing \textbf{service}, which is actually a set of resources that may come from selected providers in the system, it's possible for more than one resource with same type to make contribution to the formation of one service. No more cooperate and assembly procedure are part of pros of service and product quality will no more restricted to the worst quality of resources for the complementary effect, while the cons of service include that service can only perform specified task.
Now we can classify task and service-call into \textbf{job}, resource and service into \textbf{machine} for the follow discuss.

@@

\subsection{Metabolism mode} % (fold)
\label{sub:metabolism mode}
Metabolism mode is one extension on the original mode for platform operator to control the number of individual in the system by both restrict the arrival and eliminate the current members. As shown in \autoref{fig:metabolismmode}, 
\begin{figure}[htbp]
    \centering
    \resizebox{0.85\textwidth}{!}{\input{figures/metabolism}}
    \caption{Metabolism mode}
    \label{fig:metabolismmode}
\end{figure}
we can define machine scarcity as $\sum_jq_{\alpha,ij} - \sum_kC_{k,\tau}$.

Platform restrict the arrival of new machine by block the registration, eliminate the current machine by their quality and owner's rank.

% Rank value is initialized to $0$ and will be changed by demander's review after the finish of task:
% \begin{subnumcases}{}
% rank := rank +
% \frac{\left( p_{ij}\cdot q_{ij} \right) \left( \delta_{ij}-\gamma_{ij} \right)}{e^{\left(f_{ij} - p_{ij} -r_{ij}\right)}} & $k\in\bm{k}$\\
% \delta_{ij} = \min_{k\in\bm{k}}\left\{ \delta_k \right\} & \\
% \delta_k \sim \mathcal{N}\left(\mu_k,\sigma_k^2 \right) & $k\in\bm{k}$
% \end{subnumcases} 
% The change of rank value can be determined by:
% \begin{equation}
% 	rank := rank + \frac{ \left(\sum_{q\in\bm{q}_l}p_{ij}\cdot q \right)\left( \Delta_l -\gamma_{ij}\right) }{ e^{\left( f_{ij} - p_{ji} -r_{ij} \right)} }
% \end{equation}

\subsection{Provider schedule the jobs in machine} % (fold)
\label{sub:schedule_the_jobs_in_machine}
In order to reduce the idle rate, provider will schedule the inactive jobs on their machines. Since the schedule in service is a single machine scheduling problem that not on  what we focus in this study, we only discuss the job scheduling in resource. Since the  resource capacity dominance feature of service-call, it's necessary to suspend service-call in inactive status until all the job before it in $\mathcal{L}_{k,\tau}$ are finished, at the meantime, all the job after service-call should be stay in inactive status until the service-call is finished, as shown in \autoref{fig:simplejoblist}, service-call likes partition plate in $\mathcal{L}_{k,\tau}$.  
\begin{figure}[htbp]
	\centering
	\resizebox{.7\textwidth}{!}{\input{figures/service-call}}
	\caption{Simple illustration for one $\mathcal{L}_{k,\tau}$}
	\label{fig:simplejoblist}
\end{figure}
Therefore, we just need to schedule the tasks before the first service-call in $\mathcal{L}_{k,\tau}$ when one of the active job in $\mathcal{G}_{k,\tau}$ was finished at $\tau_0$, we denote the set of schedule task at this time as $\mathcal{L}^{(s)}_{k,\tau_0}$

\begin{table}[htbp]
  \centering
  \scriptsize
  \caption{Simple job configuration}
    \begin{tabular}{cccccc}
    \toprule
    \multicolumn{1}{c}{\multirow{2}[0]{*}{ Job}} & \multicolumn{3}{c}{Need Resource Capacity} & \multicolumn{1}{c}{\multirow{2}[0]{*}{Release Time}} & \multicolumn{1}{c}{\multirow{2}[0]{*}{Process Duration}} \\
    \multicolumn{1}{c}{} & $Type_1$ & $Type_2$ & $Type_3$ & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} \\
    \midrule
    $t_1$ & 0     & 5     & 7     & 0     & 7 \\
    $t_2$ & 7     & 5     & 7     & 4     & 5 \\
    $t_3$ & 6     & 0     & 5     & 2     & 3 \\
    $t_4$ & 9	 & 4  & 6 & 1 &2 \\
    $t_5$ & 1 & 0 & 3 & 2 & 3\\
    $sc_1$ & 0     & 0     & 3    & 1     & 1 \\
    $sc_2$ & 2     & 7     & 6     & 3     & 1 \\
    \bottomrule
    \end{tabular}%
  \label{tab:simplejobconfiguration}%
\end{table}%

Specifically, a simple instance with configuration \autoref{tab:simplejobconfiguration} and schedule chart \autoref{fig:scheduleChart} will elucidate the setting.
This instance makes some simplification in the subscript fields in order to emphasize the resource cooperation, all the job performance can only be started when all its parts are in semi-activate status, the shadow in the figure shows the waiting period between the status transitions. Horizontal dotted line constrained the available capacity of the resource for the subsequent jobs. Each finish of service-call will make the horizontal dotted line lower and it will never get higher again unless the related service is repealed.

\begin{figure}[htbp]
	\centering
	\normalsize
	\resizebox{.8\textwidth}{!}{\input{figures/scheduleChart}}
	\caption{Simple instance schedule chart with 4 resources in 3 different types}
	\label{fig:scheduleChart}
\end{figure}

In every single resource, a schedule is given by a vector of ideal finish times $\bm{f}^{(s)} = \left[f_1^{(s)}, f_2^{(s)},\dots,f^{(s)}_n\right]$,$n=\abs{\mathcal{L}^{(s)}_{k,\tau_0}\cup\mathcal{H}^{(s)}_{k,\tau_0}}$. Since the task in $\mathcal{L}^{(s)}_{k,\tau_0},\mathcal{H}^{(s)}_{k,\tau_0}$ and $\mathcal{G}_{k,\tau_0}$ may come from different orders, we here use the single uniform subscript $j$ to distinguish these tasks and their related variables, we ignore the type subscript $\alpha$ because all the job assigned here are already type matched. The schedule model is:

@@

### 2016-09-08 head.tex
draft for cfp
modify the abstract

\author[add1]{Shengkai Chen}
\author[add1,add2]{Shuiliang Fang\corref{cor1}}
% \ead{me_fangsl@zju.edu.cn}
% \address[label1]{ZJU}
% \address[label1]{Address One}
\address[add1]{Key Laboratory of Advanced Manufacturing Technology of Zhejiang Province, College of Mechanical Engineering, Zhejiang University, Hangzhou , 310027, China}
\address[add2]{The State Key Laboratory of Fluid Power Transmission and Control, College of Mechanical Engineering, Zhejiang University, Hangzhou, 310027, China}
% \author[a,b,*]{Third Author}

@@

\begin{abstract}
In cloud manufacturing, individuals engage in manufacturing business through the well-designed platform, where provider provide manufacturing resource for demander to search and purchase it. This business model allows platform operator to manage distributed massive manufacturing resources, which may help provider reduce the idle rate of their resources.
However, in such manufacturing ecosystem, the heterogeneity attribute of resource makes it tough to classify them, and the chaotic operation mode makes it hard to meet demander's need.
Cloud manufacturing ecosystem has more complicated relationship among individuals in it than that in normal manufacturing system, one individual can make decisions depend on the surroundings and others' with the help of integrated advanced technologies. Thus, in this paper, we designed an original operation mode with 3 extensions for the cloud manufacturing ecosystem to help describe some decision makings in individuals and the platform operator.
With the help of Repast Simphony, we designed an agent-based simulation model and an experiment to validate the effectiveness of these operation modes. The experiment result shows: with incubation mode, the job queue length is reduced and the resource idle rate is declined; with outsourcing mode, the job queue length is also reduced but not as much as that with incubation mode and more resource is required; with metabolism mode, lower resource is required than that with other modes and resource idle rate just rose up a little. The combination of incubation and metabolism mode is one ideal mode to maintain the manufacturing ecosystem with.
\end{abstract}

\begin{keyword}
Cloud manufacturing ecosystem \sep
Resource servitization and optimization\sep
Operation mode\sep
Manufacturing evolution\sep
Agent-based simulation

>>>>

\author[add1]{Shengkai Chen}
\author[add1,add2]{Shuiliang Fang\corref{cor1}}
% \ead{me_fangsl@zju.edu.cn}
% \address[label1]{ZJU}
% \address[label1]{Address One}
\address[add2]{The State Key Laboratory of Fluid Power Transmission and Control, College of Mechanical Engineering, Zhejiang University, Hangzhou, 310027, China}
\address[add1]{Key Laboratory of Advanced Manufacturing Technology of Zhejiang Province, College of Mechanical Engineering, Zhejiang University, Hangzhou , 310027, China}
% \author[a,b,*]{Third Author}

@@

\begin{abstract}
In cloud manufacturing, individuals engage in manufacturing business through a well-designed platform, where the operator is able to manage distributed massive manufacturing resources. 
Cloud manufacturing ecosystem has more complicated relationship among individuals in it than that in normal manufacturing system, one individual can make decisions depend on the surroundings and others'. In this paper, we designed an original operation mode with 3 extensions named incubation, outsourcing and metabolism for the ecosystem. We designed an agent-based simulation model to validate the effectiveness of these modes. Experiment result shows evolution in ecosystem: with incubation mode, the job queue length is reduced and the resource idle rate is declined; with outsourcing mode, the job queue length is also reduced but not as much as that with incubation mode and more resource is required; with metabolism mode, lower resource is required than that with other modes and resource idle rate just rose up a little.

\end{abstract}

\begin{keyword}
Cloud manufacturing ecosystem \sep
Decision making\sep
Operation mode\sep
Ecosystem evolution\sep
Agent-based simulation
